---
title: "Assessment-2"
author: "Ryosuke Otsuka s4663911"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Use the same (=clone a repository) R Project for the assignment2 as you created for Assignment1. Create a new .rmd document "Assignment2.rmd"

2. Use the provided csv file to complete the tasks below. The file needs to be uploaded to your project. You can use the variable name of your choice.


```{r}
Thanksgiving_meals <- read.csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-11-20/thanksgiving_meals.csv")
```


3.  For each question below record your answer in the markdown document that will show the question, your code and the results.
Your explanation of the data insights is VERY important as well as your code

### Part 1: formatting RMarkdown document

1. Create an Rmarkdown document with webpage as output (same as in setup)

At the start of the output document include your name in italic font and 
your student id in bold font as level 2 heading 


Separate with a solid line 

Include the title “Assignment 2” as level 1 heading 

Separate with a solid line 

List all tasks in the assignment as headings of the third level and include your results (=output) below each task showing your R code. 

**Ryosuke Otsuka** 

##s4663911

#Assignment 2


###1. Display the first 10 rows of the dataset using `kable()` function (1 marks). 

```{r}
library(tidyverse)
library(knitr)
library(skimr)

```



```{r}
kable(head(Thanksgiving_meals[, 1:10]), "pipe")
```

###2. Using `skim()` display the summary of variables. 

```{r}
skim(Thanksgiving_meals)
```


Think about the task to predict a family income based on their menu: what variables may be useful? Are all of them correct type?
Write 2-3 sentences with your explanation. (2 marks)



Think about the task to predict a community type or US_region based on their menu: what variables may be useful? Are all of them correct type? (2 marks)

3. Use `fct_reorder` and `parse_number` functions to create a factor variable `family_income`(2 mark).

```{r}
Thanksgiving_meals <- Thanksgiving_meals %>%
  mutate(family_income = fct_reorder(family_income, parse_number(age)))

```

```{r}
skim(Thanksgiving_meals)
```

4. What is the number of people who celebrate? (1 mark)

980ppl

```{r}
Thanksgiving_meals %>%
  count(celebrate, name = "people") %>%
  filter(!str_detect(celebrate, "No"))
```

5. What are categories and insights for each main dish served and the method it is prepared? (2 marks)

```{r}
Thanksgiving_meals %>%
  count(main_dish, main_prep, sort = TRUE, name = "Total") %>%
  filter(main_dish!= "I don't know", main_dish!=  "Other (please specify)", main_prep!= "I don't know",main_prep!= "Other (please specify)")%>%
  na.omit(main_dish, main_prep)
```

6. Create 3 different data viz showing insights for main dish served and the method. Provide your own legend and use themes.
Write 2-3 sentences with your explanation of each insight. (4 marks)

```{r}
library(ggplot2)

Main <- Thanksgiving_meals %>%
  filter(main_dish!= "I don't know", main_dish!=  "Other (please specify)", main_prep!= "I don't know",main_prep!= "Other (please specify)")

Main %>%
  ggplot(aes(main_dish, main_prep, col = main_dish)) +
  geom_count() + 
  coord_flip() + 
  theme_bw() +
  theme(legend.background = element_rect(fill="lightblue", 
                                  size=0.5, linetype="solid"))

```


```{r}
Main %>%
  ggplot(aes(main_dish, main_prep, col = main_dish)) +
  geom_col() + 
  theme_bw() +
  theme(legend.position='none')
```



7. How many use cranberry sauce? How many use gravy? 2marks

```{r}

```

```{r}
Thanksgiving_meals %>%
  filter(!str_detect(gravy, "No")) %>%
  count(gravy, name = "people")
```



8-9. What is the distribution of those who celebrate across income ranges. Create a data viz.
Write 2-3 sentences with your explanation of each insight. (4 marks)


```{r}
library(ggplot2)

Thanksgiving_meals %>%
  filter(!str_detect(celebrate, "No")) %>%
  filter(!str_detect(family_income, "Prefer not to answer")) -> Thanksgiving_meals_celebration

Thanksgiving_meals_celebration %>% 
  filter(!is.na(family_income)) %>%
  ggplot(aes(celebrate, family_income, col = "Yes")) + 
  geom_jitter() +
  theme_bw()

```

A family who has $125,000 to $199,999 does not tend to celebrate the thanks giving party if we compare other family. 

10. Use the following code to create a new data set 2 mark
```{r}
Type_value <- Thanksgiving_meals %>%
  select(id, starts_with("side"),
         starts_with("pie"),
         starts_with("dessert")) %>%
  select(-side15, -pie13, -dessert12) %>%
  gather(type, value, -id) %>%
  filter(!is.na(value),
         !value %in% c("None", "Other (please specify)")) %>%
  mutate(type = str_remove(type, "\\d+"))
```

11-12. Intall package `widyr` and use `pairwise_cor()` function https://www.rdocumentation.org/packages/widyr/versions/0.1.3/topics/pairwise_cor
Write 2-3 sentences with your explanation of what it does. (2 marks)

```{r}
#install.packages("widyr")
library(widyr)
library(dplyr)
```

This function can be used when we are to get the summary and test values of two different valuables that integrate together. 

Use this code for the new dataset

pairwise_cor(value, id, sort = TRUE)

```{r}
Thanksgiving_meals %>%
  filter(!is.na(community_type), 
         family_income!= "Prefer not to answer")%>%
  pairwise_cor(us_region, community_type, id, sort = TRUE)
```

Write 1 sentence with your explanation of what insights it shows. (2 marks)

It generates the collection value between community_type and us_region baced on id colum. 


13. Use `lm()` or randomForest() function to build a model that predict a family income based on data in the dataset. 8 marks

```{r}
library(modeldata)
library(tidymodels)

library(tidyverse)
library(skimr)

```

```{r}
train_test_split <- initial_split(Thanksgiving_meals)

Thanksgiving_train <- training(train_test_split)

Thanlsgiving_test <- testing(train_test_split)

```


```{r}
rec_obj <- recipe(data = Thanksgiving_train, family_income ~.)

```


```{r}
rec_obj %>%
  step_corr(all_predictors())
```

```{r}
Thanksgiving_meals_prep <- prep(rec_obj, training = Thanksgiving_train)

summary(Thanksgiving_meals_prep)
```
```{r}
Thanksgiving_meals_bake <- bake(Thanksgiving_meals_prep, Thanksgiving_train)
```

Compare 3 models using different set of input variables. Use different number of variables.

```{r}

library(randomForest)

rf <- randomForest(family_income ~ us_region + community_type, data = Thanksgiving_meals, na.action = na.omit)

print(rf)

```


Explain your choice of variables (3 sentences) 

Write 2 sentences explaining which model os best.